### 2016-12-07 local-capability-machine.tex
Add a missing title.
g1 proof in progress. Made changes to f4. Added lemma bout nsim pwl and nequality.

%Math notation
\newcommand{\restrictfun}[1]{|_{#1}}
\newcommand{\parfun}{\rightharpoonup}
\newcommand{\finparfun}{\xrightharpoonup{\textit{\tiny{fin}}}}
\newcommand{\monnefun}{\xrightarrow{\textit{\tiny{mon, ne}}}}
\newcommand{\monfun}{\xrightarrow{\textit{\tiny{mon}}}}
\newcommand{\nefun}{\xrightarrow{\textit{\tiny{ne}}}}
\newcommand{\fun}{\rightarrow}
\newcommand{\defeq}{\stackrel{\textit{\tiny{def}}}{=}}
\newcommand{\nequal}[1][n]{\stackrel{\tiny{#1}}{=}}

@@

\newcommand{\readCond}[1]{\plainfun{readCondition}{#1}}
\newcommand{\writeCond}[1]{\plainfun{writeCondition}{#1}}
\newcommand{\execCond}[1]{\plainfun{executeCondition}{#1}}
\newcommand{\entryCond}[1]{\plainfun{entryCondition}{#1}}

@@

      For convenience define let $i_1 \neq i_2$ and $i_1,i_2 \not\in \dom(\revokeTemp(W'))$ and define
      \[
        W^{(3)} = \revokeTemp{W'}\update{i_1}{\iota^\pwl_{\base_\stk'',\addrend_\stk}}\update{i_2}{\iota^\sta (\temp,\ms_\stk' |_{\start_\stk,\base_\stk''-1})}
      \]
      We now want to use the FTLR on the $\updatePcPerm{c_\adv}$ capability which is possible as we have 
      \[
        \npair[n'']{\start_\adv,\addrend_\adv} \in \readCond(\glob)(W^{(3)})
      \]
      This follows from Lemma~\ref{lem:nwlp-subset-pwl}.

@@

\subsection{Variant of the ``awkward'' example}
Assembly variant of the ``awkward'' example from \citep[p.~11]{Dreyer:2010:IHS:1863543.1863566}. 
\begin{verbatim}
g = fun _ => let x = 0 in
               fun f =>
                 x := 0;
                 f();
                 x := 1;
                 f();
                 assert(x == 1)
\end{verbatim}
\begin{lstlisting}
g1:  malloc $r_2$ 1
     store $r_2$ 0
     move $\pcreg$ $r_3$
     lea $r_3$  $\dots$
     crtcls $[(x, r_2)]$ $r_3$
     rclear $\RegName \setminus \{\pcreg,r_0,r_1 \}$
1g:  jmp $r_0$
f4:  reqglob $r1$
     reqperm $r_\stk$ $\encodePerm(\rwlx)$
     store $x$ 0
     scall $r_1$($[]$,$[r_0,r_1]$)
     store $x$ 1
     scall $r_1$($[]$,$[r_0]$)
     load $r_1$ x
     assert $r_1$ 1
     cclear $\RegName \setminus \{r_0,\pcreg\}$
4f:  jmp $r_0$
\end{lstlisting}
Where the $\dots$ is the appropriate offset to make the capability point to \texttt{f4}.

\begin{lemma}[Correctness of $g1$]
      \label{lem:correctness-g1}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\olf) \\
    c_{g1} & \defeq ((\entry,\local),\mathtt{g1}-\olf,\mathtt{4f},\mathtt{g1}) \\
    c_\stk & \defeq ((\rwlx,\local),\start_\stk,\addrend_\stk,\start_\stk-1) \\
    c_\malloc & \defeq ((\entry,\glob),\start_\malloc,\addrend_\malloc,\start_\malloc+\olf) \\
    \reg & \in \Regs \\
    m & \defeq \hs_{g1} \uplus 
        \ms_\flag \uplus                
        \ms_\link \uplus 
        \ms_\adv \uplus 
        \ms_\malloc \uplus 
        \ms_\stk \uplus
        \ms_{\var{frame}} 
  \end{align*}
  where 
  \begin{align*}
    &\dom(\hs_{g1}) = [\mathtt{g1}-\olf,\mathtt{4f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]}
  \end{align*}
  and
  \begin{itemize}
  \item $\ms_{g1}(\mathtt{g1}-\olf) = ((\readonly,\glob),\link,\link,\link)$, $\ms_{g1}(\mathtt{g1}-\olf+1) = ((\readwrite,\glob),\flag,\flag,\flag)$, the rest of $\hs_{g1}$ contains the code of $g1$ immediately followed by the code of $f4$.
  \item $\ms_\flag = [\flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\link \mapsto c_\malloc]$
  \item $\hs_\adv$ contains a read-write capability for $\hs_\link$ on its first address and otherwise it consists only of instruction.
  \end{itemize}
  if 
  \[
    (\reg\update{\pcreg}{c_\adv}\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}},m) \step[n] (\halted,m'),
  \]
  then
  \[
    m'(\flag) = 0
  \]  
\end{lemma}
\lau{If $c_{g1}$ is global it seems like we will run into trouble. When we have to prove $\npair{c_{g1}} \in \stdvr(W)$}

@@

\begin{lemma}
  \begin{align*}
    &\forall n,W_1,W_2,W_1' \ldotp
    &\quad W_1 \nequal W_2 \land W_1' \futurestr W_1 \Rightarrow \exists W_2' \ldotp W_2' \nequal W_1' \land W_2' \futurestr W_2
  \end{align*}
\end{lemma}

@@

>>>>

%Math notation
\newcommand{\restrictfun}[1]{|_{#1}}
\newcommand{\parfun}{\rightharpoonup}
\newcommand{\finparfun}{\xrightharpoonup{\textit{\tiny{fin}}}}
\newcommand{\monnefun}{\xrightarrow{\textit{\tiny{mon, ne}}}}
\newcommand{\monfun}{\xrightarrow{\textit{\tiny{mon}}}}
\newcommand{\nefun}{\xrightarrow{\textit{\tiny{ne}}}}
\newcommand{\fun}{\rightarrow}
\newcommand{\defeq}{\stackrel{\textit{\tiny{def}}}{=}}
\newcommand{\nequal}[1][n]{\stackrel{\tiny{#1}}{=}}
\renewcommand{\nsim}[1][n]{\stackrel{\tiny{#1}}{\simeq}}

@@

\newcommand{\readCond}[1]{\plainfun{readCondition}{#1}}
\newcommand{\writeCond}[1]{\plainfun{writeCondition}{#1}}
\newcommand{\execCond}[1]{\plainfun{executeCondition}{#1}}
\newcommand{\entryCond}[1]{\plainfun{enterCondition}{#1}}

@@

      For convenience define let $i_1 \neq i_2$ and $i_1,i_2 \not\in \dom(\revokeTemp{W'})$ and define
      \[
        W^{(3)} = \revokeTemp{W'}\update{i_1}{\iota^\pwl_{\base_\stk'',\addrend_\stk}}\update{i_2}{\iota^\sta (\temp,\ms_\stk' |_{\start_\stk,\base_\stk''-1})}
      \]
      We now want to use the FTLR on the $\updatePcPerm{c_\adv}$ capability which is possible as we have 
      \[
        \npair[n'']{\start_\adv,\addrend_\adv} \in \readCond{}(\glob)(W^{(3)})
      \]
      This follows from Lemma~\ref{lem:nwlp-subset-pwl}.

@@

\subsection{Variant of the ``awkward'' example}
Assembly variant of the ``awkward'' example from \citep[p.~11]{Dreyer:2010:IHS:1863543.1863566}. 
\begin{verbatim}
g = fun _ => let x = 0 in
               fun f =>
                 x := 0;
                 f();
                 x := 1;
                 f();
                 assert(x == 1)
\end{verbatim}
\begin{lstlisting}
g1:  malloc $r_2$ 1
     store $r_2$ 0
     move $\pcreg$ $r_3$
     lea $r_3$ $\dots$
     crtcls $[(x, r_2)]$ $r_3$
     rclear $\RegName \setminus \{\pcreg,r_0,r_1 \}$
1g:  jmp $r_0$
f4:  reqglob $r1$
     reqperm $r_\stk$ $\encodePerm(\rwlx)$
     store $x$ 0
     scall $r_1$($[]$,$[r_0,r_1,r_{\var{env}}]$)
     store $x$ 1
     scall $r_1$($[]$,$[r_0,r_{\var{env}}]$)
     load $r_1$ x
     assert $r_1$ 1
     mclear $r_\stk$
     cclear $\RegName \setminus \{r_0,\pcreg\}$
4f:  jmp $r_0$
\end{lstlisting}
\lau{todo: when the stack is received the first time, make sure it points to where we would expect it to point (1 - range of auth.) Make macro for this.}
Where the $\dots$ is the appropriate offset to make the capability point to \texttt{f4}.

\begin{lemma}[Correctness of $g1$]
      \label{lem:correctness-g1}
  For all $n \in \nats$
  let
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\olf) \\
    c_{g1} & \defeq ((\entry,\glob),\mathtt{g1}-\olf,\mathtt{4f},\mathtt{g1}) \\
    c_\stk & \defeq ((\rwlx,\local),\start_\stk,\addrend_\stk,\start_\stk-1) \\
    c_\malloc & \defeq ((\entry,\glob),\start_\malloc,\addrend_\malloc,\start_\malloc+\olf) \\
    m & \defeq \hs_{g1} \uplus 
        \ms_\flag \uplus                
        \ms_\adv \uplus 
        \ms_\stk \uplus
        \ms_{\var{frame}} 
    &\dom(\hs_{g1}) = [\mathtt{g1}-\olf,\mathtt{4f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]}
  and
  \item $\ms_{g1}(\mathtt{g1}-\olf) = ((\readonly,\glob),\link,\link,\link)$, $\ms_{g1}(\mathtt{g1}-\olf+1) = ((\readwrite,\glob),\flag,\flag,\flag)$, the rest of $\hs_{g1}$ contains the code of $g1$ immediately followed by the code of $f4$.
  \item $\ms_\flag = [\flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\link \mapsto c_\malloc]$
  \item $\hs_\adv$ contains a read-write capability for $\hs_\link$ on its first address and otherwise it consists only of instruction.
  if 
    (\reg_0\update{\pcreg}{c_\adv}\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}},m) \step[n] (\halted,m'),
  then
    m'(\flag) = 0
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:correctness-g1}]
  Let $n$ be given and make the remaining assumptions of the lemma. Define
    W = & [0 \mapsto \iota^\sta (\perma,\ms_{g1})]\\
        & [1 \mapsto \iota^\sta (\perma,\ms_\flag)]\\
        & [2 \mapsto \iota^\sta (\perma,\ms_\link)]\\
        & [3 \mapsto \iota^\pwl]\\
        & [4 \mapsto \iota^{\nwl,p}_{\start_\adv,\addrend_\adv}] \\
        & [5 \mapsto \iota_{\malloc,0}]
    \ms = \ms_{g1} \uplus 
        \ms_\flag \uplus                
        \ms_\adv \uplus 
        \ms_\stk
  and use the FTLR on $c_\adv$ (possible due to lemma~\ref{lem:nwlp-subset-pwl} and the chose world). From this, we get
    \npair[n+1]{c_\adv} \in \stder(W).
  Assuming we can show $\npair[n+1]{\reg_0\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}}} \in \stdrr(W)$ and $\memSat[n+1]{\ms}{W}$, then we know
    \npair[n+1]{(\reg_0\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}}\update{\pcreg}{c_\adv},\ms) \in \observations(W)}
  Using $\ms_{\var{frame}}$ and resulting memory $m$ and the assumption from the lemma that
    (\reg_0\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}}\update{\pcreg}{c_\adv},m) \step[n] (\halted,m')
  We get some $W_{\var{final}} \futurestr W$, $\ms'$, and $\ms_r$ such that
    & m' = \ms' \uplus \ms_r \uplus \ms_{\var{frame}}\\
    & \memSat[1]{\ms'}{W_{\var{final}}}
  From island 1 (the flag island), the above memory segment satisfaction, and the fact that $W_{\var{final}} \futurestr W$ we get that part of $\ms'$ must be $\ms_\flag$ and thus
    m'(\flag) = 0
  which is the desired result. Now it suffices to show:
    \item $\memSat[n+1]{\ms}{W}$
      %TODO - this should be similar to previous proofs
    \item $\npair[n+1]{\reg_0\update{r_\stk}{c_\stk}\update{r_1}{c_{g1}}} \in \stdrr(W)$
        \item Case $r \in \RegName \setminus \{\pcreg,r_\stk,r_1,\}$: amounts to $\npair[n+1]{0} \in \stdvr(W)$, trivial.
        \item Case $\npair[n+1]{c_\stk} \in \stdvr(W)$:
          % TODO - same as in previous proof.
        \item Case $\npair[n+1]{c_{g1}} \in \stdvr(W)$:\\
          let $n' < n+1$ and $W' \futurestr W$ be given and show
            \npair[n']{\updatePcPerm{c_{g1}}} \in \stder(W')
          to this end let $n'' \leq n'$, $\ms'$, and $\reg'$ be given and assume
          \begin{align}
            & \npair[n'']{\reg'} \in \stdrr(W') \label{g1:regrel1} \\
            & \memSat[n'']{\ms'}{W'} \label{g1:memsat1}
          \end{align}
            \npair[n'']{(\reg'\update{\pcreg}{\updatePcPerm{c_{g1}}},\ms')} \in \observations(W')
          To this end let $i \leq n''$, $\ms_f$, $m''$ be given and assume
          \begin{equation}
            (\reg'\update{\pcreg}{\updatePcPerm{c_{g1}}},\ms' \uplus \ms_f) \step[i] (\halted,m'') \label{g1:execution}
          \end{equation}
          \begin{equation}
            \exists W_{\var{str}}' \futurestr W', ms_r, \ms'' \ldotp m'' = \ms'' \uplus \ms_r \uplus \ms_f \land \memSat[n''-i]{\ms''}{W_{\var{str}}'} \label{g1:g-goal}
          \end{equation}
          consider how the above execution goes. By \ref{g1:memsat1} we know that the instructions of $g1$ are unaltered. The following happens
            \item ...
            %TODO - typeout the details. 
          In the end, we have a new memory segment
            \ms'' = \ms_\malloc' \uplus \ms_x \uplus \ms_{\var{env}} \uplus \ms_{\var{cls}}
          where $\ms_x(x) = 0$, $\ms_{\var{env}}(\var{env}) = ((\rwx,\glob),x,x,x)$, and $\ms_{\var{cls}}=[\var{cls} \mapsto c_{\var{env}}, \var{cls} + 1 \mapsto c_{f4}, \var{cls} + 2 \mapsto i^{ac}_1, \var{cls} + m + 1 \mapsto i^{ac}_m]$ where $i^{ac}_1, \dots, i^{ac}_m$ are the instructions of the activation code, $c_{\var{env}} = ((\rwx,\glob),\var{env},\var{env},\var{env})$, $c_{f4} = ((\exec,\glob),\mathtt{g1}-\olf,\mathtt{4f},\mathtt{f4})$.
          Further at this point, the register file contains:
            \reg'' = reg_0\update{\pcreg}{\updatePcPerm{\reg'(r_0)}}\update{r_0}{\reg'(r_0)}\update{r_1}{((\entry,\glob),\var{cls},\var{cls} + m + 1,\var{cls}+2)}
          We know that $\npair[n'']{\reg'(r_0)} \in \stdvr(W')$. We have assumed execution does not fail, so $\reg'(r_0)$ must be a capability with permission $\entry$, $\exec$, $\rwx$, or $\rwlx$. In either case, we get $\execCond{}$ or $\entryCond{}$ (for certain parameters). Now use $n^{(3)}$ ($n''$ minus the steps the two malloc calls used) and $W'' \futurewk W'$ where
            W'' = W'\update{5}{\iota_\malloc'}
                    \update{i_1}{\iota^\sta (\perm,\ms_{\var{env}})}
                    \update{i_2}{\iota^\sta (\perm,\ms_{\var{cls}})}
                    \update{i_3}{\iota_x}
          where $i_1,i_2,i_3 \not\in\dom(W')$ and they distinct, and $\iota_\malloc \futurewk W(5)$ and
            \iota_x & = (\perm,0,\{(0,1),(0,0),(1,1)\},\{(1,0),(0,1),(0,0),(1,1)\},H_x) \\
            H_x \; s \; W & = \{\npair{\ms} \mid \ms(x) = s \land \dom(\ms) = [x,x]\}
          %TODO insert tikz picture of machine (just like Dreyer Neis machine.)
          with $\execCond{}$ or $\entryCond{}$ to get
            \npair[n^{(3)}]{\updatePcPerm{\reg'(r_0)}} \in \stder(W'')
          If we can show $\npair[n^{(3)}]{\reg''} \in \stdrr(W'')$ and $\memSat[n^{(3)}]{\ms''}$, then using assumption \ref{g1:execution} we can get \ref{g1:g-goal}.

          SFTS:
          \begin{enumproof}
            \item$\memSat[n^{(3)}]{\ms''}$
              %TODO should be simple - all existing regions have interpretations monotone wrt public future worlds. The malloc island uses its "isolation condition" which makes room for the two new islands. The x islands starts in state 0 (and the appropriate memory address contains 0). The env and cls islands are static islands designed to accept exactly what the memory contains.
            \item $\npair[n^{(3)}]{\reg''} \in \stdrr(W'')$ amounts to showing:
              \begin{enumproof}
                \item For $r \in \RegName \setminus \{\pcreg, r_0, r_1 \}$ $\reg''(r) = 0$ and it is trivial to show $\npair[n^{(3)}]{0} \in \stdvr(W'')$. 
                \item $\npair[n^{(3)}]{\reg'(r_0)} \in \stdvr(W'')$ - follows from \ref{g1:regrel1} and public monotonicity of $\stdvr$.
                \item $\npair[n^{(3)}]{((\entry,\glob),\var{cls},\var{cls} + m + 1,\var{cls}+2)} \in \stdvr(W'')$ \\
                  To this end let $n^{(4)} < n^{(3)}$, $W^{(3)} \futurestr W''$ be given and assume
                  \begin{align*}
                    \\ \npair[n^{(4)}]{\reg^{(3)}} \in \stdrr(W^{(3)}) &
                    \\ \memSat[n^{(4)}]{\ms^{(3)}}{W^{(3)}} \label{g1:memsat-cls}
                  \end{align*}
                  for some $\reg^{(3)}$ and $\ms^{(3)}$ and show
                  \[
                    \npair[n^{(4)}]{(\reg^{(3)}\update{\pcreg}{((\exec,\glob),\var{cls},\var{cls} + m + 1,\var{cls}+2)},\ms^{(3)})} \in \observations(W^{(3)})
                  \]
                  to this end let $j \leq n^{(4)}$, $m^{(3)}$, and $m_f'$ be given and assume
                  \begin{equation}
                    (\reg^{(3)}\update{\pcreg}{((\exec,\glob),\var{cls},\var{cls} + m + 1,\var{cls}+2)},\ms^{(3)} \uplus \ms_f') \step[j] (\halted, m^{(3)}) \label{g1:execution2}
                  \end{equation}
                  and show
                  \begin{equation}
                    \exists W_{\var{str}}^{(3)} \futurestr W^{(3)}, \ms'^{(3)}, \ms_r \ldotp m^{(3)} = \ms'^{(3)} \uplus \ms_r \uplus \ms_f' \land \memSat[n^{(4)}-j]{\ms'^{(3)}}{W_{\var{str}}'} \label{g1:g-goal2}
                  \end{equation}
                  to this end consider what happens in execution \ref{g1:execution2}: Due to \label{g1:memsat-cls} we know that the activation code and $f4$ code is unaltered. Running the activation code loads the environment capability to $r_{\var{env}}$ and loads the $f4$ capability, then the $r_1$ register is tested whether it contains a global capability and the $r_\stk$ register is tested for whether it contains an $\rwlx$ capability, say $\reg''(r_\stk) = ((\rwlx, \gl), \start_{\stk}', \addrend_{\stk}', \addr_{\stk}')$. As we know the execution halts succesfully, both of these checks must succeed.

                  Continuing execution until just after the point where we jump to the capability in register $r_1$ will store $0$ to address $x$ of memory, push restore code, $\reg^{(3)}(r_0)$, $\reg^{(3)}(r_1)$, push $\reg^{(3)}(r_\stk)$, and a capability to return to in $f4$.

                  The memory and register file at this point are as follows: %TODO
                  \[
                  \dots  
                  \]

                  We have assumed that the execution does not fail which entails several things: The capability in $r_1$ is executable after being jumped to. The capability $r_\stk$ has authority over some none empty part of the memory.

                  The latter is used with Lemma~\ref{lem:pwl-nsim-view}

                  As $\reg^{(3)}(r_\stk) = ((\rwlx,\gl),\start,\addrend,\addr)$ for some $\gl$, $\start$, $\addrend$, and $\addr$ and $\npair[n^{(4)}]{\reg^{(3)}(r_\stk)} \in \stdvr(W^{(3)})$ we know that
                  \begin{align*}
                    \\ \npair[n^{(4)}]{(\start,\addrend)} \in \readCond{}(\gl)(W) &
                    \\ \npair[n^{(4)}]{(\start,\addrend)} \in \writeCond{}(\iota^\pwl,\gl)(W)
                  \end{align*}
                  which means that for some region $r$ and interval $[\start',\addrend'] \supseteq [\start,\addrend]$ we have 
                  \[
                    W(r) \nsim[n^{(4)}] \iota^\pwl_{\start',\addrend'}
                  \]

              \end{enumproof}
          \end{enumproof}
      \end{enumproof}
  \end{enumproof}
\end{proof}

\lau{If $c_{g1}$ is global it seems like we will run into trouble. When we have to prove $\npair{c_{g1}} \in \stdvr(W)$ - for now g1 is global (then we will see if it gives any troubles later on)}

@@

\begin{lemma}
  \begin{align*}
    &\forall n,W_1,W_2,W_1' \ldotp
    &\quad W_1 \nequal W_2 \land W_1' \futurestr W_1 \Rightarrow \exists W_2' \ldotp W_2' \nequal W_1' \land W' \futurestr W_2
  \end{align*}
\end{lemma}

@@

\begin{lemma}
  \label{lem:pwl-nsim-view}
  \begin{align*}
    & \forall n \in \nats \ldotp \forall \start, \addrend, b \in \Addrs \ldotp \forall \iota \in \Regions \\
    & \iota \nsim \iota^\pwl_{\start,\addrend} \land a \leq b \Rightarrow \iota \nequal \iota^\pwl_{\start,\addrend}
  \end{align*}
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:pwl-nsim-view}]
  For $n = 0$ it is trivial, so assume $n > 0$.
  Say $\iota = (v,s,\phi_{\var{pub}},\phi,H)$, then by $\nsim$, we know $s = 1$, $\phi_{\var{pub}} \equiv \phi \equiv =$, and $H = H^\pwl_{\start,\addrend}$. It remains to show that $v=\temp$. To do so, we show that it cannot be the case that $v=\perma$. If $v = \perma$, then $H$ must be monotone with respect to $\futurestr$. If we can show that this is not the case, then for $\iota$ to be a region it must be the case that $v \neq \perma$ and thus $v = \temp$.

To this end let $b\not\in[\start,\addrend]$ and define the worlds:
\begin{align*}
  \xi (W)  =& [0 \mapsto \iota^\pwl_{\start,\addrend}]  \\ 
      & [1 \mapsto \iota^\pwl_{b,b}] \\
  \xi (W')  =& [0 \mapsto \iota^\pwl_{\start,\addrend}]  \\ 
      & [1 \mapsto \revoked] 
\end{align*}
For these two worlds, we have $\xi(W') \futurestr \xi(W)$ and from mono.\ of $\xi^{-1}$ $W' \futurestr W$. Now define the following memory segment:
\[
  \ms = [\start \mapsto ((\readonly,\local),b,b,b), \start+1 \mapsto 0, \dots , \addrend \mapsto 0]
\]
It is the case that
\[
  \npair{\ms} \in H \; 1 \; W
\]
but
\[
  \npair{\ms} \not\in H \; 1 \; W'
\]
as it is not the case that \lau{what if $n=1$? Need to figure out when exactly this holds}
\[
  \npair[n-1]{((\readonly,\local),b,b,b)} \in \stdvr(\xi(W')).
\]
The only other option that remains is $v=\temp$.
\end{proof}
\lau{$a \leq b$ that the interpretation is not empty.}
